Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex
add captions for tables, fix typos

% TODO explain tables
\begin{table*}[t]
	\centering
	\caption{My caption}
	\small
	\label{within-subject-table}
	\begin{tabular}{c|c|c|c|c|c|c|c|c|}
		\cline{2-9}
		& \multicolumn{4}{c|}{Memorability} & \multicolumn{2}{c|}{Belivability} & \multicolumn{2}{c|}{Desirability} \\ \cline{2-9} 
		& \begin{tabular}[c]{@{}c@{}}video\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}video\\ trip\end{tabular} & photo & video & photo & video \\ \hline
		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
		\multicolumn{1}{|c|}{\%} & 0.97 & \multicolumn{2}{c|}{0.50} & 0.54 & 0.78 & 0.80 & 0.11 & 0.15 \\ \hline
		\multicolumn{1}{|c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 96.987$\\ p = 0.0001\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 0.41$\\ p = 0.2611\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 214) = 0.02$\\ p = 0.4434\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356 ) = 0.995$\\ p = 0.1593\end{tabular}} \\ \hline
	\end{tabular}
\end{table*}

@@

	\caption{My caption}

@@

\multicolumn{1}{|c|}{\multirow{-6}{*}{Belivability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline

>>>>

% TODO explain tables
\begin{table*}[t]
	\centering
	\caption{Participant responses about the memorability, believability, and desirability or Rewinds and photos. The aggregate responses for the two mediums are compared.}
	\small
	\label{within-subject-table}
	\begin{tabular}{c|c|c|c|c|c|c|c|c|}
		\cline{2-9}
		& \multicolumn{4}{c|}{Memorability} & \multicolumn{2}{c|}{Believability} & \multicolumn{2}{c|}{Desirability} \\ \cline{2-9} 
		& \begin{tabular}[c]{@{}c@{}}video\\  location\end{tabular} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}photo\\ location/trip\end{tabular}} & \begin{tabular}[c]{@{}c@{}}video\\ trip\end{tabular} & photo & video & photo & video \\ \hline
		\multicolumn{1}{|c|}{N} & 177 & \multicolumn{2}{c|}{179} & 177 & 86 & 128 & 179 & 177 \\ \hline
		\multicolumn{1}{|c|}{\%} & 0.97 & \multicolumn{2}{c|}{0.50} & 0.54 & 0.78 & 0.80 & 0.11 & 0.15 \\ \hline
		\multicolumn{1}{|c|}{p-val} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 96.987$\\ p = 0.0001\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356) = 0.41$\\ p = 0.2611\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 214) = 0.02$\\ p = 0.4434\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 356 ) = 0.995$\\ p = 0.1593\end{tabular}} \\ \hline
	\end{tabular}
\end{table*}

@@

	\caption{Differences in memorability, believability, and desirability for different conditions of the trip or traveller. A green background denotes cases where there was a statistically significant difference within that condition.}

@@

\multicolumn{1}{|c|}{\multirow{-6}{*}{Believability}} & \multicolumn{1}{c|}{\multirow{-3}{*}{video}} & p-val & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 2.917$ \\ p = 0.0483\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{ACDDAA}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 128) = 5.835$ \\ p = 0.0079\end{tabular}} & \multicolumn{2}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 127) = 1.865$ \\ p =0.086\end{tabular}} & \multicolumn{6}{c|}{\cellcolor[HTML]{FFFFC7}\begin{tabular}[c]{@{}c@{}}$\chi^2(5, 128) = 10.093$ \\ p = 0.0726\end{tabular}} & \multicolumn{2}{c|}{\begin{tabular}[c]{@{}c@{}}$\chi^2(1, 91) = 0.951$ \\ p = 0.1647\end{tabular}} \\ \hline
